\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb,amsthm}
\usepackage{dsfont}
\usepackage{bbold}
\usepackage{cancel}

\title{Random Graphs Project 2}
\author{Alex Rose, Pedro Rodriguez}
\date{Marh 2016}

\begin{document}

\maketitle

\section{Random Graph Coupling}

Let $E$ be the probability of an edge existing in the union graph, and $E_i$ the probability of an edge existing in graph $i$.

\subsection{}
$P(E) = P(E_1 \lor E_2) = P(E_1) + P(E_2) - P(E_1 \land E_2) = p_1 + p_2 -p_1p_2$.

\subsection{}
$P(E) = 1 - P(\neg E_1 \land \neg E_2 \land ... \land \neg E_n) = 1 - (1-p_1)(1-p_2)...(1-p_n) = 1 - q$ 


\section{Threshold Function Existence Proof}

For this section, let $f_n(p) = \mathbb{P}(G_{n,p} \models A)$ and $g_n(p) = \mathbb{P}(G_{n,p} \cancel{\models} A) = 1 - f_n(p)$.

\subsection{}
Consider $a$ to be the set of graphs in $G_{n,p}$ with the monotone property $A$. Since each graph is distinct,

$$P(G_{n,p}\vDash A)=\sum_{G_i\in a} P(G_{n,p}=G_i)$$

Since there are a finite number of graphs in the state space of $G_{n,p}$, the sum is finite. Therefore, if we prove that the inner probability is continuous, this is a finite sum of continuous functions which is itself continuous.

The probability of any particular $G_i\in G_{n,p}$ is defined as $P(G_i)=p^{c}q^{{n\choose 2}-c}$ where $c\in [0,{n\choose 2}]$. For a particular $G_i$, its existence is calculated by success of $c$ edges existing times ${n\choose 2}-c$ edges not existing. Since this function is continuous with respect to $p$, the probability of $P(G_{n,p}\vDash A)$ is also continuous.

\subsection{}
$f_n(0) = 0$ and $f_n(1) = 1$, and $f_n(t)$ is continuous. So by the Intermediate Value Theorem, $\exists p_n$ such that $f_n(p_n) = \frac{1}{2}$.

\subsection{}
Proof by induction. At $k = 1$, the expression is $[1-(1-p) \le 1*p] \rightarrow [p \le p]$. Suppose the expression is true at $k = n$ i.e $[1-(1-p)^k \le np]$. Then for $k = n+1$:

$$1-(1-p)^{n+1} \le (n+1)p \rightarrow 1 - (1-p)^n + p(1-p)^n \le np + p \rightarrow p(1-p)^n \le p $$ 
$$\rightarrow (1-p)^n \le 1$$

And $(1-p)^n < 1$ holds for all $0 \le p \le 1$ and $n \ge 1$. So the expression is true by induction.

\subsection{}
Consider graphs $G_1,...,G_k$ and $P(G_i\vDash A)$. Note that a union graph includes all its subgraphs, so by definition if the monotone property holds for an individual graph, it also holds for the union graph as well. Therefore, we observe from the inclusion-exclusion principle and that each graph is generated from the same $G_{n,p}$ that:

\begin{align*}
P(G_1\vDash A \vee ... \vee G_k\vDash A)&\le P(\cup_{i=1}^k G_i\vDash A)\\
1-P(G_1\nvDash A \wedge ... \wedge G_k\nvDash A)&\le P(\cup_{i=1}^k G_i\vDash A)\\
1-P(G_p\nvDash A)^k&\le P(\cup_{i=1}^k G_i\vDash A)\\
P(\cup_{i=1}^kG_i\vDash A)&=P(G_{1-q}\vDash A), q=\prod_{i=1}^k(1-p)=(1-p)^k\\
P(\cup_{i=1}^kG_i\vDash A)&=P(G_{1-(1-p)^k}\vDash A)\\
\text{Since P is continuous and from 2.3}\\
P(G_{1-(1-p)^k}\vDash A)&\le P(G_{kp}\vDash A)\\
1-P(G_p\nvDash A)^k\le P(\cup_{i=1}^k G_i\vDash A)&=P(G_{1-(1-p)^k}\vDash A)\le P(G_{kp}\vDash A)\\
1-P(G_p\nvDash A)^k&\le P(G_{kp}\vDash A)\\
1-P(G_{kp}\vDash A)&\le P(G_p\nvDash A)^k\\
P(G_{kp}\nvDash A)&\le P(G_p\nvDash A)^k\qed \\
\end{align*}

\subsection{}
From (2.4), we have $g_n(kp) < g_n(p)^k$ for integer $k \ge 1$ and $0 \le p \le 1$. So $g_n(\left \lfloor{k_n}\right \rfloor p_n) \le g_n(p_n)^{\left \lfloor{k_n}\right \rfloor}$, and as $g_n(p_n) = \frac{1}{2}$: 

$$\lim_{n\to\infty} g_n(p_n)^{\left \lfloor{k_n}\right \rfloor} = \lim_{n\to\infty} \frac{1}{2}^{\left \lfloor{k_n}\right \rfloor} = 0$$

So $g_n(\left \lceil{k_n}\right \rceil p)$ goes to 0.

\subsection{}
As $g_n$ is monotonically decreasing, $g_n(kp) \le g_n(\left \lfloor{k_n}\right \rfloor p)$. So as $g_n(\left \lfloor{k_n}\right \rfloor p)$ goes to 0 as $n \to \infty$, $g_n(kp)$ also goes to 0.

\subsection{}
$\lim_{n\to\infty} g_n(\frac{p_n}{k_n}) = 1$ is equivalent to $\lim_{n\to\infty} f_n\left(\frac{p_n}{k_n}\right)=0$. As $p_n$ is bounded, $\lim_{n\to\infty} \frac{p_n}{k_n} = 0$. So:

$$\lim_{n\to\infty} f_n\left(\frac{p_n}{k_n}\right) = f_n(0) = 0 \rightarrow \lim_{n\to\infty} g_n\left(\frac{p_n}{k_n}\right) = 1$$.

\subsection{}
Let $T(n) = p_n$ be the threshold function. If $p(n) >> T(n)$, $p(n)$ is of the form $k_n p_n$, where $(k_n)_{n \ge 1} \to \infty$, by definition of the $>>$ operator. (2.6) showed $\lim_{n\to\infty} g_n(k_n p_n) = 0$, which implies $\lim_{n\to\infty} f_n(p(n)) = 1$ if $p(n) >> T(n)$.\\

Likewise; if $p(n) << T(n)$, $p(n)$ is of the form $\frac{p_n}{k_n}$ by definition of the $<<$ operator. (2.7) showed $\lim_{n\to\infty} g_n(\frac{p_n}{k_n}) = 1$, which implies $\lim_{n\to\infty} f_n(p(n)) = 0$ if $p(n) << T(n)$. So by the definition of a threshold function, $T(n) = p_n$ is a threshold function of A.

\end{document}